
Loading all the basic packages
```{r}
require(pacman) 
pacman::p_load(pacman,plm,rethinking,dplyr,GGally,ggplot2,ggthemes,ggvis,httr,lubridate,plotly,rio,rmarkdown,shiny,stringr,tidyr,gplots,car,estimatr)
```
Loading data,removing companies with misleading names and declaring data to be panel
```{r}
data<-import("C:/Users/91875/Desktop/Sem 2/Finance/FM_Project_data_Final_v1.csv")
data<-data[!(data$Company=="TEAM" | data$Company=="SIRI"| data$Company=="FB"| data$Company=="EBAY"),]

data.p<-pdata.frame(data,index=c("Date","Company"))
str(data)
```


Exploring Panel data
```{r}
plotmeans(R~Company,  main="Heterogeneity across stocks", data=data) 
plotmeans(R~Date, main="Heterogeneity across weeks", data=data)
```
```{r}
my_df <- data.frame(x = data$AGSVI, y = data$R, group = data$Company)

ggplot(my_df, aes(x = x, y = y)) +
  geom_point(aes(colour = group)) + # Points and color by group
  scale_color_discrete("Groups") +  # Change legend title
  xlab("AGSVI") +              # X-axis label
  ylab("Return")  +             # Y-axis label
  theme(axis.line = element_line(colour = "black", # Changes the default theme
                                 size = 0.24))
```

```{r}
my_df <- data.frame(x = data$AGSVI, y = data$R, group = data$Company)

ggplot(my_df, aes(x = x, y = y)) +
  geom_point(aes(colour = group)) + # Points and color by group
  scale_color_discrete("Groups") +  # Change legend title
  xlab("AGSVI") +              # X-axis label
  ylab("Return")  +             # Y-axis label
  theme(axis.line = element_line(colour = "black", # Changes the default theme
                                 size = 0.24))
```
Running panel models

1.Pooled OLS Regression
a)Estimation happens through OLS
b)similar to cross sectional analysis, basically ignoring the time-series aspect
c)Assumption: Error variance is uniform across cross-sections


Returns V/s AGSVI,lagged Return(just to see how AGSVI affect change in Returns from one week to another),Volatility(R^2) and a bunch of factors

Model 1.a--> r(t,i)=alpha+beta_1*agsvi(t,i)+beta_2*r(t-1,i)+beta_3*r^2(t-1,i)+beta_4*Mkt_RF+beta_5*SMB+beta_6*HML+beta_7*RMW+beta_8*CMA+ε(t,i)

```{r}
model_1.a<-plm(R~R_lag1+AGSVI+Volatility+SMB+HML+RMW+CMA+Mkt_RF,data=data.p,model="pooling")
summary(model_1.a)
```


Plotting the result
```{r}
plot(data$AGSVI, data$R, pch=19, xlab="AGSVI", ylab="R") 
abline(plm(R~R_lag1+AGSVI+Volatility+SMB+HML+RMW+CMA+Mkt_RF,data=data.p,model="pooling"),lwd=3, col="red")
```

Volume traded V/s AGSVI, lagged Volume(just to see how agsvi affect volume change from one week to another),Volatility(R^2) and a bunch of factors

Model 1.b--> volume(t,i)=alpha+beta_1*agsvi(t,i)+beta_2*volume(t-1,i)+beta_4*Mkt_RF+beta_5*SMB+beta_6*HML+beta_7*RMW+beta_8*CMA+ε(t,i)
```{r}
model_1.b<-plm(log(Volume)~log(Volume_lag1)+AGSVI+SMB+HML+RMW+CMA+Mkt_RF,data=data.p,model="pooling")
summary(model_1.b)
```
2.Controlling for Stock fixed effects- Within model/Fixed Effects and Random effects model

a)Treats the unobserved individual heterogeneity (alpha_i) for each stock to be correlated with explanatory variables.
b)FE estimation involves a transformation to remove the unobserved effect alpha_i prior to estimation. On the time-demeaned eqn, OLS is applied.
              
              y(i,t)=beta_1*x(i,t)+alpha(i)+u(i,t)-->1
              
              On averaging this eqn over time
              
              y(i')=beta_1*x(i')+alpha(i)+u(i')-->2
              
             (y(i,t)-y(i'))=beta_1*(x(i,t)-x(i'))+u(i,t)-u(i')
             
c)Only focuses on variations within stocks. All differences between stocks are controlled for. Comparing single stock to itself at different periods of time.All time invariant variables vanish.
d)The coefficient tells us how much returns changes in a week, on an average per stock, when agsvi is increased by 1 unit
e)Errors won't be correlated over time
f) For RE, we assume correlation(alpha(i),X(i))=0 
g)Each individual stock has a different intercept, but we are not gona let it be whatever it wants to be. Its gonna follow normal dist.
h) RE has more assumptions so small SE

Returns V/s AGSVI,lagged Return(just to see how agsvi affect change in Returns from one week to another),Volatility(R^2) and a bunch of factors, but controlled for stock-fixed effects (k_i)

Model 2.a/b--> r(t,i)=alpha+beta_1*agsvi(t,i)+beta_2*r(t-1,i)+beta_3*r^2(t-1,i)+beta_4*Mkt_RF+beta_5*SMB+beta_6*HML+beta_7*RMW+beta_8*CMA+k_i+ε(t,i)

FE Model
```{r}
model_2.a<-plm(R~R_lag1+AGSVI+Volatility+SMB+HML+RMW+CMA+Mkt_RF,data=data.p,model="within")
summary(model_2.a)
```
RE Model
```{r}
model_2.b<-plm(R~R_lag1+AGSVI+Volatility+SMB+HML+RMW+CMA+Mkt_RF,data=data.p,model="random")
summary(model_2.b)
```

Run a Hausman test comparing fixed and random effects 

```{r}
phtest(model_2.a,model_2.b)
```
We favor FE model in this case 

Volume V/s AGSVI,lagged Volume(just to see how agsvi affect change in Volume from one week to another),Volatility(R^2) and a bunch of factors, but controlled for stock-fixed effects (k_i)

Model 2.c/d--> Volume(t,i)=alpha+beta_1*agsvi(t,i)+beta_2*Volume(t-1,i)+beta_4*Mkt_RF+beta_5*SMB+beta_6*HML+beta_7*RMW+beta_8*CMA+k_i+ε(t,i)

```{r}
model_2.c<-plm(log(Volume)~log(Volume_lag1)+AGSVI+SMB+HML+RMW+CMA+Mkt_RF,data=data.p,model="within")
summary(model_2.c)
```

```{r}
model_2.d<-plm(log(Volume)~log(Volume_lag1)+AGSVI+SMB+HML+RMW+CMA+Mkt_RF,data=data.p,model="random")
summary(model_2.d)
```
Run a Hausman test comparing fixed and random effects 

```{r}
phtest(model_2.c,model_2.d)
```
We favor FE model in this case 

3. Controlling for both stock (between) and time (within) fixed effects

Returns V/s AGSVI,lagged Return(just to see how agsvi affect change in Returns from one week to another),Volatility(R^2) and a bunch of factors, but controlled for stock and time fixed effects (k(i) and v(t))
                 
                 r(t,i)=alpha+beta_1*agsvi(t,i)+beta_2*r(t-1,i)+beta_3*r^2(t-1,i)+beta_4*Mkt_RF+beta_5*SMB+beta_6*HML+beta_7*RMW+beta_8*                        CMA+v(t)+k(i)+ε_(t,i)
 
```{r}
model_3.a<-plm(R~R_lag1+AGSVI+Volatility+SMB+HML+RMW+CMA+Mkt_RF+factor(Date),data=data.p,model="within")
summary(model_3.a)

```
Same model but using dummy variables (just to check if results are same)
```{r}
model_4.a<-lm(R~R_lag1+AGSVI+Volatility+SMB+HML+RMW+CMA+Mkt_RF+factor(Date)+factor(Company),data=data)
summary(model_4.a)
```

Volume V/s AGSVI,lagged Volume(just to see how agsvi affect change in Returns from one week to another),Volatility(R^2) and a bunch of factors, but controlled for stock and time fixed effects (k(i) and v(t)) using Dummy variables
                 
                 Volume(t,i)=alpha+beta_1*agsvi(t,i)+beta_2*Volume(t-1,i)+beta_4*Mkt_RF+beta_5*SMB+beta_6*HML+beta_7*
                             RMW+beta_8*CMA+v(t)+k(i)+ε_(t,i)


 
```{r}
model_3.b<-plm(log(Volume)~log(Volume_lag1)+AGSVI+SMB+HML+RMW+CMA+Mkt_RF+factor(Date),data=data.p,model="within")
summary(model_3.c)

```